2024 US Presidential Election Forecast Model

### 2024-11-04 paper/paper.qmd
Update by Doran
-Change the type of csv to parquet
-Change the clean_data.R

library(tidyverse)
library(readr)
library(dplyr)
library(knitr)

clean_data <- read_csv("../data/01-raw_data/clean_data.csv")
nyt_data <- read_csv("../data/02-analysis_data/NYT_data.csv")
cleaned_data <- read_csv("../data/02-analysis_data/cleaned_data.csv")
model_data <- read_csv("../data/02-analysis_data/cleaned_data.csv")
```

>>>>

library(tidyverse)
library(readr)
library(dplyr)
library(knitr)
library(arrow)

nyt_data <- read_parquet("../data/02-analysis_data/NYT_data.parquet")
cleaned_data <- read_parquet("../data/02-analysis_data/cleaned_data.parquet")
model_data <- read_parquet("../data/02-analysis_data/cleaned_data.parquet")
```
